Overlapping Batches for the Assessment of Solution Quality in Stochastic Programs

### 2013-10-23 omrp.tex
non Times Roman font
minor changes to abstract and keywords

\usepackage{latexsym}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{enumerate}
\usepackage{mathptmx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{amsthm}
\usepackage[pdftex,colorlinks=true,urlcolor=blue,citecolor=black,anchorcolor=black,linkcolor=black]{hyperref}
\usepackage{setspace}

@@

\begin{abstract}
\noindent The method of Overlapping Batch Means (OBM) has long been used in simulation as a method of reusing data to generate estimators with asymptotically lower variance.
In this paper, we extend the OBM method to stochastic programming by formulating a variant of the multiple replications procedure used for assessing solution quality.
We show conditions under which the resulting optimality gap estimators are strongly consistent, and have the same asymptotically lower variance as the classical results.
Computational results for several test problems are presented, examining the small-sample behavior of the overlapping batches method.\smallskip

\Keywords{Sample average approximation; Optimality gap estimation; Overlapping batches; Stochastic programming}
\end{abstract}

>>>>

\usepackage{latexsym}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{enumerate}
%\usepackage{mathptmx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{amsthm}
\usepackage[pdftex,colorlinks=true,urlcolor=blue,citecolor=black,anchorcolor=black,linkcolor=black]{hyperref}
\usepackage{setspace}

@@

\begin{abstract}
\noindent Overlapping Batch Means (OBM) has long been used in simulation as a method of reusing data to generate variance estimators with asymptotically lower variance.
In this paper, we extend the OBM method to stochastic programming by formulating a variant of the multiple replications procedure used for assessing solution quality.
We show conditions under which the resulting optimality gap estimators are strongly consistent, and have the same asymptotically lower variance as the classical results.
Computational experiments for several test problems are presented, examining the small-sample behavior of the overlapping batches method in this context.\smallskip

\Keywords{Sample average approximation (SAA); Overlapping batch means;   Stochastic programming; Optimality gap estimation}
\end{abstract}
